|

### 2024-10-28 output/seminar-slideshow.qmd
Improve 3d plot with camera view and tooltip

::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  5
#| fig-height: 5
PROB_AXIS_2D <- seq(-3, 3, by = .1)

@@

plot_ly(
  x = ~PROB_AXIS_2D,
  y = ~PROB_AXIS_2D,
  z = ~mirt_prob_surface,
  colorscale = list(c(0, 1), PALETTE_BLUE["normal"] |> rep(2)),
  type = 'surface',
  showscale = FALSE,
  hoverinfo = 'none'
) |>
  layout(
    scene = list(
      xaxis = list(title = "<i>θ</i><sub>1</sub>"),
      yaxis = list(title = "<i>θ</i><sub>2</sub>"),
      zaxis = list(title = "P(I<sub>k</sub> = 1)"),
      camera = list(
        center = list(z = -.2),
        eye = list(x = -.12, y = -1.8, z = 1)
      )
    )
  ) |>
  config(
    displayModeBar = FALSE,
    scrollZoom = FALSE,
    mathjax = 'cdn'
  )
```
:::

>>>>

::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  4.6
#| fig-height: 4.6
PROB_AXIS_2D <- seq(-3, 3, by = .1)

@@

plot_ly(
  x = ~PROB_AXIS_2D,
  y = ~PROB_AXIS_2D,
  z = ~mirt_prob_surface,
  colorscale = list(c(0, 1), PALETTE_BLUE["normal"] |> rep(2)),
  type = 'surface',
  hovertemplate = 'P(I<sub>k</sub> = 1) = %{z:.2f}<extra></extra>',
  showscale = FALSE,
  hoverinfo = 'Z'
) |>
  layout(
    scene = list(
      xaxis = list(title = "<i>θ</i><sub>1</sub>"),
      yaxis = list(title = "<i>θ</i><sub>2</sub>"),
      zaxis = list(title = "P(I<sub>k</sub> = 1)"),
      camera = list(
        center = list(x = -.1, z = -.2),
        eye = list(x = -.12, y = -1.8, z = 1)
      )
    )
  ) |>
  config(displayModeBar = FALSE, scrollZoom = FALSE)
```
:::
